STA610 Case Study 1 Team 4 Report

### 2021-03-21 Draft Report 3.21.Rmd
draft

---
title: "STA610 Case Study 1 Team 4 Report"
author:
- Cole Juracek (Coordinator)
- Lauren Palazzo (Programmer)
- Lingyu Zhou (Checker)
- Fan Zhu (Presenter)
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

@@

load("~/Documents/Spring 2021/STA 610 - H Models/cs1/streetrx.RData")
df <- streetrx %>% filter(api_temp=="oxymorphone", !is.na(ppm))
```

@@

summary(mod_s)
# summary(mod_c)
# summary(mod_r)

LR <- 2*(logLik(mod_s)-logLik(mod_c))
0.5*(1-pchisq(LR[1],1)+1-pchisq(LR[1],1)) # choose s over c

@@

```{r}
mod_final <- lmer(data=df_filter, log_ppm ~ (dose_per_mg |state) + dose_per_mg + bulk_purchase, REML=F)

@@

@@

```{r}
View(data.frame(table(df$state, df$bulk_purchase)))
```

>>>>

---
title: "STA610 Case Study 1 Team 4 Report"
author:
- Cole Juracek (Coordinator)
- Lauren Palazzo (Programmer)
- Lingyu Zhou (Checker)
- Fan Zhu (Presenter)
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

load("streetrx.RData")
df <- streetrx %>% filter(api_temp=="oxymorphone", !is.na(ppm))
```

@@

summary(mod_s)
# summary(mod_c)
# summary(mod_r)
BIC(mod_s)
BIC(mod_c)
BIC(mod_r)
LR <- 2*(logLik(mod_s)-logLik(mod_c))
0.5*(1-pchisq(LR[1],1)+1-pchisq(LR[1],1)) # choose s over c

@@

## Changes start here

```{r}
mod_final <- lmer(data=df_filter, log_ppm ~ (dose_per_mg |state) + dose_per_mg + bulk_purchase, REML=F)
BIC(mod_final)

#model with no random slope is better
#best model!!!
mod_final <- lmer(data=df_filter, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + source, REML=F)
BIC(mod_final)
#8412.338

#class model
mod1 <- lmer(data=df_filter, log_ppm ~ (1 | state) + date_num + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F)
BIC(mod1)

@@

resqq <- plot_resqq(mod_final)
ranefci <- plot_ranef(mod_final)
#take a long time to run
#resi <- plot_redres(mod_final, type = "std_cond")
grid.arrange(resqq, ranefci, ncol = 3)
```

@@

## Results
#### Fixed Effects
```{r, message=FALSE}
#knitr::kable(fixef(mod1))
#confint(mod1)[3:11,]

# extract coefficients
coefs <- data.frame(coef(summary(mod_final)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
knitr::kable(coefs, col.names = c("Estimate", "Std.Error", "t-value", "P-value"))
```

#### need to change numbers after finalizing model
* date_num: For the date_num variable, controlling for other variables, for every one unit increase in the date_num, the price per mg of oxymorphone reduces by a multiplicative effect of exp(-0.0001290) =  0.999871, about a 0.0129% decrease.

* mgstr: For the mgstr variable, controlling for for other variables, for every one unit increase in mgstr, the price per mg of oxymorphone reduces by a multiplicative effect of exp(-0.0241262) =  0.9761625, about a 2.38375% decrease.

* bulk_purchase: “Not bulk purchase” is the reference group.
  * Controlling for other variables, being bulk purchase reduces the price per mg by a multiplicative effect of exp(-0.161) = 0.8521, about a 14.79% reduction.

* Primary_Reason: “Primary_Reason: Other or Unknown” is the reference group. 
  * Controlling for other variables, taking oxymorphone with the primary reason of self-treating increase the price per mg by a multiplicative effect of exp(0.05) = 1.0513, about a 5.13% increase than the price per mg of oxymorphone for people whose primary reason is “other or unknown”. 
  * Controlling for other variables, taking oxymorphone with the primary reason of enjoyment tends to increase the price per mg by a multiplicative effect of exp(0.2) = 1.221403, about a 22.1403% increase than the price per mg of oxymorphone for people whose primary reason is “other or unknown”.

* source: “Source: Unknown” is the reference group.

  * Controlling for other variables, purchasing oxymorphone with Internet source tends to increase the price per mg by a multiplicative effect of exp(0.02) = 1.0202, about a 2.02% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with personal source tends to increase the price per mg by a multiplicative effect of exp(0.07) = 1.0725, about a 7.25% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with “heard it” source tends to increase the price per mg by a multiplicative effect of exp(0.24) = 1.2712, about a 27.12% increase than the price per mg of oxymorphone for people with unknown drug source.

#### Random Effects
```{r}
#VarCorr(mod1)
Variance <- c(0.04748, 0.96369)
Std.Dev <- c(0.2179, 0.9817)
Groups <- c("state (Intercept)", "Residual")

REvar <- cbind(Groups, Variance, Std.Dev)

knitr::kable(REvar, col.names = c("Group", "Variance", "Std.Dev"))
```
The within-state variance $\sigma^2$ is 0.96369, which is much larger than the across-state variance $\tau^2$, 0.04748.

```{r, include=FALSE}
library(sjstats)
icc(mod_final)
```

```{r}
ICC <- 0.047
knitr::kable(ICC, col.names = "Intraclass Correlation")
```
Intraclass correlation is 0.047, which means values are not very similar from the same state.

```{r, fig.align='center', fig.height=8}
dotplot(ranef(mod_final, condVar=TRUE))$state
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Nevada is the lowest and this intercept is also significant.

## Appendix
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
